SubsidyExplorer - Step 2: Create Vessel List

### 2020-08-07 scripts/02_vessel_list.Rmd
plots

pie_theme <- normal_theme +
  theme(
    axis.line = element_blank(),
    axis.title.x = element_blank(),
    axis.text = element_blank(),
    axis.title.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks = element_blank()  )

# Total number of vessels
n_gear_type_plot <- vessels_by_gear %>%
  mutate(vessel_class = fct_re)
ggplot(vessels_by_gear)+
  aes(x = vessel_class, y = count, fill = vessel_class)+
  geom_bar(stat = "identity", width = 1, color = "grey4", size = 0.2)+
  #coord_polar("y")+
  #scale_fill_tableau(name = "Flag State", palette = "Tableau 20")+
  normal_theme+
  labs(title = paste0("Number of vessels by class | Total vessels: ", format(sum(vessels_by_gear$count), big.mark = ",")))+
  labs(x = "Gear Type", y = "Number of Vessels")+
  guides(fill = "none")+
  coord_flip()+
  scale_y_continuous(expand = c(0,0))

# Flags using each gear types
ggplot(vessels_by_gear)+
  aes(x = fct_reorder(vessel_class, flag_states, .desc = TRUE), y = flag_states, fill = vessel_class)+
  geom_bar(stat = "identity", width = 1, color = "grey4", size = 0.2)+
  scale_y_continuous(expand = c(0,0))+
  scale_fill_discrete(guide = "none")+
  normal_theme +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(title = paste0("Number of flag states using each vessel class | Total vessels: ", format(sum(vessels_by_gear$count), big.mark = ",")),
       x = "Vessel Class",
       y = "Number of Flag States")
}
```

>>>>

# Total number of vessels by gear type
n_gear_type_plot <- vessels_by_gear %>%
  mutate(vessel_class = fct_reorder(vessel_class, count)) %>%
  ggplot()+
  aes(x = vessel_class, y = count, fill = vessel_class)+
  geom_bar(stat = "identity", width = 1, color = "grey4", size = 0.2)+
  #coord_polar("y")+
  #scale_fill_tableau(name = "Flag State", palette = "Tableau 20")+
  normal_theme+
  labs(title = paste0("Number of vessels by gear type | Total vessels: ", format(sum(vessels_by_gear$count), big.mark = ",")))+
  labs(x = "Gear Type", y = "Number of Vessels")+
  guides(fill = "none")+
  coord_flip()+
  scale_y_continuous(expand = c(0,0))

ggsave(paste0(results_dir, "n_vessels_gear_type_plot.png"), n_gear_type_plot, width = 7.5, height = 6, units = "in")

# Total number of vessels by flag
vessels_by_flag_gear <- vessel_list_out %>%
  group_by(flag_iso3, vessel_class) %>%
  summarize(count = n_distinct(ssvid),
            fao_regions = n_distinct(fao_region),
            length_avg = mean(length_m, na.rm = T),
            tonnage_avg = mean(tonnage_gt, na.rm = T),
            engine_power_avg = mean(engine_power_kw, na.rm = T),
            fishing_hours = sum(fishing_hours_eez_fao_ter, na.rm = T),
            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T)) %>%
  mutate(tot_count = sum(count)) %>%
  ungroup()

n_flag_plot <- vessels_by_flag_gear %>%
  mutate(flag = fct_reorder(countrycode(flag_iso3, "iso3c", "country.name"), tot_count)) %>%
  ggplot()+
  aes(x = flag, y = log(count), fill = vessel_class)+
  geom_bar(stat = "identity", width = 1, color = "grey4", size = 0.2)+
  #coord_polar("y")+
  #scale_fill_tableau(name = "Flag State", palette = "Tableau 20")+
  normal_theme+
  labs(title = paste0("Number of vessels by flag state and gear type | Total vessels: ", format(sum(vessels_by_gear$count), big.mark = ",")))+
  labs(x = "Flag State", y = "log(Number of Vessels)", fill = "Gear Type")+
  coord_flip()+
  scale_y_continuous(expand = c(0,0))+
  theme(axis.text.y = element_text(size = 4, angle = 20))

ggsave(paste0(results_dir, "n_vessels_flag_gear_type_plot.png"), n_flag_plot, width = 7.5, height = 10, units = "in")
}
```
